
Simple Random Sampling

Generating 150 samples of values 0 and 1 with a repetition parameter, and setting a 50% probability for each variable.
```{r}
amostra=sample(c(0,1),150,replace=TRUE, prob=c(0.5,0.5))
amostra
summary(as.factor(amostra))
```

Changing the probability of the variables, increasing the percentage for variable '0'. Setting the display to 70%.
```{r}
amostra = sample(c(0,1),150,replace=TRUE, prob=c(0.7,0.3))
amostra
summary(as.factor(amostra))
```
Notice that there was an increase in the probability adjustment made; now, variable '0' is being displayed more often.

Let's analyze the same initial scenario, but now with 1000 cases instead of just 150.
```{r}
amostra = sample(c(0,1),1000,replace = TRUE, prob = c(0.5,0.5))
amostra
summary(as.factor(amostra))
```


Now let's explore other contexts.

If you need random data from a specific database you're working with, you can set up a random sequence of indices to apply to the dataset search filter. Let's exemplify below.
```{r}
amostra = sample(c(0,1),150,replace = TRUE, prob = c(0.7,0.3))
summary(as.factor(amostra))
```
We have created a list of 150 indices with random values of 0 and 1, with a probability of 70% for the value 0 and 30% for the value 1. Now, we will move on to the next step.

Let's develop a variable that will receive the value of the position that satisfies the condition that the sample value is equal to 1. Below is the result.
```{r}
amostrairis = iris[amostra==1,]
amostrairis
```
Therefore, only the rows of the iris dataset whose sample database row value resulted in 1 will be displayed. This will result in the automatic display of 48 values from the iris dataset.

Okay. But if I run this process again, I get a new random combination of 48 rows. What do I need to do to save this data and prevent it from being changed if I run it again? Below is a demonstration of how to "save" the generated random values.

Using the "set.seed" function in R, you can set a random number generation seed. This ensures that when you run the code again, the results will be reproducible, following the same sequence of random values defined by the seed.

```{r}
set.seed(1)
sample(c(1000),1)
```
Now let's test again to see if the value will be the same.
```{r}
set.seed(1)
sample(c(1000),1)
```

